---
title: "INFINITy report"
output:
  html_document:
    theme:
      bg: "#FFFFFF"
      fg: "#4e79cb"
      primary: "#ffc72c"
      secondary: "#ee65cd"
      base_font:
        google: "Prompt"
      code_font:
        google: "JetBrains Mono"
---

This report was created using the **INFINITy: a machine learning-based web application for human influenza A & B virus classification v`r version()`** software for subtyping of Human Influenza HA sequences.<br />

<h2>

Run stats

</h2>

Run was performed on `r Sys.Date()`.<br /> from which **`r as.character(length(data_reactive()$data_out$Label))`** sequences were selected for analysis.<br />

<h2>

Output table

</h2>

The following table lists the sequences under analysis and the corresponding classification results.

```{r,echo=FALSE, warning=FALSE,message=FALSE}

col<-"#ee65cd"
    col2<-"#ffc72c"
    table<-table()
    datatable(table,selection = 'single',
              style = 'bootstrap',
              extensions = 'Buttons',
              options = list(
                columnDefs = list(list(targets = c(5,7,8), visible = FALSE)),
                dom = 'Bfrtip',
                lengthMenu = list(c(5, 15, -1), c('5', '15', 'All')),
                pageLength = 15,
                buttons =
                  list('copy', 'print', list(
                    extend = 'collection',
                    buttons = list(
                      list(extend = 'csv', filename = paste(input$file[1,1],"INFINITy_results"),sep=""),
                      list(extend = 'excel', filename = paste(input$file[1,1],"INFINITy_results"),sep=""),
                      list(extend = 'pdf', filename = paste(input$file[1,1],"INFINITy_results"),sep="")),
                    text = 'Download'
                  ),
                list(
                  extend = "collection",
                  text = 'Show All',
                  action = DT::JS("function ( e, dt, node, config ) {
                                    dt.page.len(-1);
                                    dt.ajax.reload();
                                }")
                ))
              ))%>%formatStyle("Length","Length_QC",backgroundColor = styleEqual(c(0, 1), c(col2, col)))%>% 
                   formatStyle("N","N_QC",backgroundColor = styleEqual(c(0, 1), c(col2, col)))%>%                                         
                   formatStyle("Probability","Probability_QC",backgroundColor = styleEqual(c(0, 1), c(col2, col)))    
```

<h2>

Classification models

</h2>

The following table lists the models used for the classification.

```{r,echo=FALSE, warning=FALSE,message=FALSE}


model1_data<-model_table()
  datatable(model1_data)
```
